%________________________________________________________________________________________
% @brief	LaTeX2e Resume for Kamil K Wojcicki
% @author   Kamil K Wojcicki
% @url	  http://linux.dsplabs.com.au/?p=54
% @date	 Decemebr 2007
% @info	 Based on Latex Resume Template by Chris Paciorek
%		   http://www.biostat.harvard.edu/~paciorek/


%________________________________________________________________________________________
\documentclass[margin,line]{resume}
\usepackage{hyperref}
\hypersetup{pdfborder={0,0,0}}
\begin{document}
\name{Daniel Enman, B.Sc}
\begin{resume}


	%____________________________________________________________________________________
	% Contact Information
	\section{\mysidestyle Contact\\Information}\vspace{2mm}

	\begin{tabular}{@{} l @{\hspace{38mm}} r}
						& +1 (902) 754-8288\\
						& \href{mailto:enmand@gmail.com}{enmand@gmail.com} \\
						& \href{http://github.com/enmand}{http://github.com/enmand}\\
	\end{tabular}


	%____________________________________________________________________________________
	% Research Interests
	\section{\mysidestyle About\\Me}
		I am a graduate of St. Francis Xavier University in Mathematics and Computer Science. I have worked on a number of different projects, large and small, ranging from web and software development and systems administration to research and analysis. I've also made contributions to open source projects, and continue to find ways to contribute to the open source community.

	\section{\mysidestyle Thesis}
		(2010) B. Sc Thesis: ``An Introduction to Projective Geometry: Conics''. Supervised by T. Bruen, Mathematics Statistics and Computer Science, St. Francis Xavier University


	%____________________________________________________________________________________
	% Education
	\section{\mysidestyle Education}

	{\bf Saint Francis Xavier University}, Antigonish, Nova Scotia \vspace{2mm}%
	\begin{list1}
		\item[] B. Sc Advanced Major in Mathematics
		\begin{list2}
			\vspace*{1mm}
			\item Participated in the ACM programming contest at APICS 2009
			\item Participated in the William Lowell Putnam Mathematics competition
		\end{list2}
		\item[] Partial list of Mathematical/Computer Science Courses taken:
		\begin{list2}
			\vspace*{1mm}
			\item Calculus I/II/III and Vector Calculus
			\item Real Analysis I/II
			\item Complex Variables
			\item Partial Differential Equations
			\item Discrete Mathematics and Combinatorics
			\item Modern (Abstract) Algebra
			\item Mathematical Modelling
			\item Probability and Mathematical Statistics
			\item Data Structures
			\item Algorithm Analysis
			\item Object Oriented Programming Paradigm
			\item Operations Research
			\item Computational Physics
		\end{list2}
		\vspace*{2mm}
		\item[] High School Diploma (High Honours), Prince Andrew High School, June 2006
		\begin{list2}
			\vspace*{1mm}
			\item Received award for recognition in Computer Science
		\end{list2}
	\end{list1}

	%____________________________________________________________________________________
	% Professional Experience
	\section{\mysidestyle Professional\\Experience}

	{\bf znanja Inc.} \vspace{2mm}\\\vspace{1mm}
	{\sl Co-Founder \& CTO} \hfill {January 2012 -- February 2014}
	\\
		My role at znanja is partially a continuation of my work at Velsoft. znanja is an eLearning platform, that blends content conversion with content delivery into a platform that allows instructors, training facilitators and others to create, convert and deliver their content in real-time, and deliver it to their students in an easy, customizable and effective way. My responsibilities at znanja as co-CTO are to work with the rest of the engineering, marketing and sales team to define, develop and deliver a top-notch eLearning platform. This platform is built using a multitude of technologies including: Linux, SmartOS (Solaris 10), Python, Node.JS, C++, JavaScript.

		Additionally, part of my role is to communicate with our customers, and our support team to balance our product with the needs of our customers, as well as provide customers with the best experience we can offer. This includes communicating with large enterprise customers as well as small and medium sized businesses to figure out, and help implement ideal solutions to each unique problems some organizations present.
\newpage
	{\bf Velsoft Training Materials Inc.} \vspace{2mm}\\\vspace{1mm}
	{\sl Sr. Software \& Infrastructure Engineer} \hfill {\bf April 2010 -- March 2012}
	\\
		My role at Velsoft was a varied one, and one that was continually changing and expanding. My chief responsibility here is as a software and infrastructure engineer. In this role, I worked with our development and our systems team to develop amazing eLearning applications on our own eLearning platform, while enhancing and expanding the platform itself. This afforded me a great deal of experience with the entire stack, ranging from our Linux and Solaris servers, to the Python, C++, NodeJS and PHP codebase. Given that we dealt with large amounts of content and data, we continually found and developed ways of viewing, and analysing that data to provide a comprehensive overview of our platform's health, customer's content, student responses and scoring, as well as help to define overall customer strategies.

		Additional to my role as an engineer, I also managed the team of software and systems engineers and the overall infrastructure that they rely on, on a day-to-day basis, including both our internal infrastructure, and our external customer facing infrastructure. Our internal infrastructure existed in-house, and consisted of all types of servers ranging from our directory server (Active Directory on Windows Server 2008 R2) to our project management suite (the Atlassian suite including JIRA, Confluence and Bamboo) and our development infrastructure. The external interface existed on a combination of Amazon AWS (EC2, S3, Route53) and Joyent's SmartDataCenter hosted privately. My team also managed internal services such as VPN, GPO and workstation management, and customer facing services behind OAuth 2.0, such as our Courses API and our eLearning API.

%	At Velsoft, one of my responsibilities is for the deployment, administration and upkeep of the network infrastructure both internally and externally. This includes administrating, or overseeing many Linux servers, and several Windows 2008 R2 servers some of which of each are in an Active Directory forest that is shared with client computers internally. These computers interact with a number of network resources including a VPN for developers, a file server, printer server, development servers, application servers and project management with wiki suite to provide a comprehensive network environment suitable for large scale collaboration, planning, development and testing.

%	Additionally, I lead a team of developers in both their day-to-day software maintenance, software development and on a number of large scale projects. As the senior developer, I am responsible for planning, developing and deploying a scalable eLearning platform using OAuth 2.0 for content delivery, a number of different packaging formats (including SCORM 1.2) for interoperability and a built-in-house learning management system (``LMS'') to deliver eLearning as a software as a service (``SaaS'') solution. This role includes deploying and configuring any required services including Apache, MySQL, MongoDB, memcache and Subversion on a large cluster of servers, hosted on Amazon's AWS platform. The system is set up in an effective and efficient manner so as to serve hundreds of thousands of requests per-day. Additional projects include in-house applications for sales and marketing, and developing an API to interact with both our master courses database and our master SCM that houses our course content.

	Velsoft has provided me the opportunity to build and develop scalable, high-use applications built on a number of technologies, including NodeJS, and Amazon's AWS cloud. At Velsoft I grew both as a developer, and as a manager. I have managed and developed with large teams, and small teams. I have also lead in the release of patches back to the open source community, and the open sourcing of many of the libraries we use internally.

	{\bf Freelance and Open-Souce Developer} \vspace{2mm}\\\vspace{1mm}%
	{\sl DevOps Engineer and Consultant} \hfill {\bf 2004 -- present}\\
	I have been working as a freelance and open-source developer for a number of years, and have worked on many open-source projects, including as co-lead developer on the Cerenkov framework (now defunct). I have developed numerous websites using this framework. I also have experience with other frameworks, including the Zend Framework, and KohanaPHP. Many of my open source contributions can be found on my GitHub account at \href{https://github.com/enmand}{https://github.com/enmand}.

	I have done PHP Development work for some local and non-local companies including;
	\begin{list2}
		\item Highland Multimedia (\href{http://highlandmultimedia.com}{http://highlandmultimedia.com})
%		\item Hodder Consulting (\href{http://yourwizard.ca}{http://yourwizard.ca})
		\item Impact Communications (\href{impactcommunications.ca/}{http://impactcommunications.ca})
	\end{list2}

	%Some of my previous work includes:
	%\begin{list2}
	%	\item Nova Scotia Liberal Caucus (\href{http://nsliberalcaucus.ca}{http://nsliberalcaucus.ca})
	%	\item FORCE (\href{http://fundyforce.ca}{http://fundyforce.ca})
	%\end{list2}

	A small sample of my work includes patches for the following projects:
	\begin{list2}
		\item Kohana PHP Framework
		\item SVN PECL
		\item nodesvn (https://github.com/enmand/nodesvn)
		\item nodegears (https://github.com/enmand/nodegears)
	\end{list2}

%	{\bf Saint Francis Xavier University (TSG)}, Antigonish, Nova Scotia \vspace{2mm}\\\vspace{1mm}%
%	{\sl Student System Administrator (Intern)} \hfill {\bf January 2010 -- April 2010 (1 semester)}\\
%	My role at the Technology Support Group for my last semester at St. Francis Xavier University was on the Projects Team of the Infrastructure Technology department. I had been tasked with multiple projects, from researching virtualization technologies such as VMWare to researching and testing Windows 7 and Windows 2008 Server rollout options on a large scale to all of the client computer labs (using KMS and MAK for activation). As a \textit{student system administrator}, I interacted daily the Manager of Technology Infrastructure and provided suggestions on a number of projects.

	\newpage

	{\bf Gatemaster, Inc.}, Halifax, Nova Scotia \vspace{2mm}\\\vspace{1mm}%
	{\sl Software Developer (Intern)} \hfill {\bf July 2009 -- Aug 2009 (summer term)}\\
	With Gatermaster, Inc. I was responsible for helping build a new ``Internet Rental Listings'' website, where landlords and tenants could connect with each other in new ways. One of the tasks I was charged with was creating the Tenant ``Application Centre'' where applicant tenants could create and store information on their application. Along with the ``Application Centre'', I was also partially responsible (together with the Sr. Software Developer) for helping put the system together in its entirety. The development work was mainly in PHP, though there was a significant amount of JavaScript (using the jQuery library). The database used to store and process the large amount of information was Firebird.

%	{\bf St. Francis Xavier Students’ Union (\href{http://theu.ca}{TheU})}, Antigonish, Nova Scotia \vspace{2mm}\\\vspace{1mm}%
%	{\sl Lead Web Developer} \hfill {\bf April 2009 -- March 2010}\\
%	At TheU.ca, I am responsible for developing and maintaining TheU.ca websites, sub-websites (such as the Frosh site), and all services offered over Internet (or local network), along with updating and maintaining TheU.ca’s servers (the web server running CentOS 5.3, the development server running Debian 5.0 and the file server running OS X Server) under the direction of the VP-Communications. I was responsible for creating and maintaining the Frosh Week website, the Frosh Kit Distrobution system, as well as the photo gallery, as well as setting up and maintaining the file server and backup solution. A voting system my partner Ben and I created was utilized in the latest Student Union elections polling stations to ensure that voting was fair and that people were properly tracked. The St. Francis Xavier Students' Union has the largest voter turnout of any Canadian University.

%	{\bf Saint Francis Xavier University (TSG)}, Antigonish, Nova Scotia \vspace{2mm}\\\vspace{1mm}%
%	{\sl Contact Centre Representative} \hfill {\bf November 2007 - January 2010}\\
%	At the TSG, I was responsible for answering calls, emails and faxes to assist with the TSGs regular duties around the University, as they are responsible for nearly all the technology on campus. My duties involved helping to troubleshoot users with any problems, updating assigned student's accounts passwords, as well as documentation on subjects concerning the technologies that the TSG has implemented.

%	{\bf IDEA Group}, Calgary, Alberta \vspace{2mm}\\\vspace{1mm}%
%	{\sl Computer Support} \hfill {\bf May 2008 -- July 2008} \\
%	At IDEA Group, I was responsible for rebuilding and supporting all the workstations and mobile stations, as well as assisting Metaphore, who took care of the servers and server software. I was also responsible for making sure all the workstations were up-to-date and stable, and for helping to manage the licenses on each computer.

	% Just to make it look nicer

%	{\bf Global Skills Inc.}, Halifax, Nova Scotia \vspace{2mm}\\\vspace{1mm}%
%	{\sl Contract Work} \hfill {\bf April 2008}\\
%	In the month of April 2008 Global Skills Inc. contacted me to upgrade a server for a Pontiac Buick
%	car dealership in Halifax, Nova Scotia. I was responsible for upgrading the system memory, as well
%	as ensuring the server was otherwise up-to-date.

%	{\bf Staples Business Depot}, Dartmouth, Nova Scotia \vspace{2mm}\\\vspace{1mm}%
%	{\sl Aisles Associate} \hfill {\bf 2005-2006}\\
%		At Staples Business Depot, I was responsible for assisting customers needs with their
%		office supply, and sometimes with their technological needs. I was also responsible for
%		ensuring that the aisles were clean, well kept, and stocked at all times.

	%____________________________________________________________________________________
	% Computer Skills
	\section{\mysidestyle Computer\\Skills}
	Programming Languages
	\begin{list2}
		\vspace*{1mm}
		\item Python
		\begin{list2}
			\item Python 3
			\item Python 2
			\item Pyramid
			\item Django
			\item SQLAlchemy
		\end{list2}
		\item Ruby
		\begin{list2}
			\item Rails (Ruby on Rails)
		\end{list2}
		\item JavaScript
		\begin{list2}
			\vspace*{1mm}
			\item Backbone.js
			\item Underscore.js
			\item jQuery
		\end{list2}
		\item PHP
%		\begin{list2}
%			\vspace*{1mm}
%			\item KohanaPHP
%			\item MVC (Model-View-Controller) pattern
%			\item ORM (Object-relational mapping)
%			\item Object-Oriented methodologies
%			\item PHP4 and PHP5 experience (including PHP5.3)
%		\end{list2}
		\item Node.JS (and V8 core)
		\item HTML (HTML5, CSS3, etc)
		\item C
		\item C++

		\item Database (relational and ``NoSQL'')
		\begin{list2}
			\item PostgreSQL
			\item MongoDB
			\item Redis
			\item MySQL
			\item Firebird
			\item ORACLE 9i
		\end{list2}
		\item Java
	\end{list2}

	Operating Systems
	\begin{list2}
		\vspace*{1mm}
		\item Linux (including Ubuntu, Debian, ArchLinux, Gentoo)
		\item Solaris (Illumos, SmartOS, OpenIndiana)
		\item FreeBSD (6-RELEASE and pfSense)
		\item Mac OS X, including OS X Server
		\item Microsoft Windows (7, 2008 Server R2)
	\end{list2}

	Miscellaneous
	\begin{list2}
		\item OpsCode Chef (Using ``chef-solo'')
		\item Juniper ScreenOS 6.3
		\item IPSec, OpenVPN
		\item Gearman/Asyncronous job processing
		\item Memcached and caching algorithms
		\item Working knowledge of OAuth, OAuth2.0 and Hawk
		\item Working knowledge of SCORM 1.2 and SCORM 2004
	\end{list2}
	%\begin{list2}
	%	\item SCORM 2004 and SCORM 1.2
	%\end{list2}
\newpage

	%____________________________________________________________________________________
	% Referees
%	\section{\mysidestyle Referees}
%		{\sl Available on request.}


%________________________________________________________________________________________
\end{resume}
\end{document}

%________________________________________________________________________________________
% EOF

